The following chapter will give a more detailed introduction in the structure of Traveling Salesman.\newline

As already mentioned, Traveling Salesman is designed following a modular architecture. Every essential or optional type of module is defined by a java interface with basic methods to provide its desired functionality. The most important ones in our project are

\begin{itemize}

	\item Interface \texttt{IDataSet}
	
		\texttt{IDataSet} provides methods to store and receive Openstreetmap map elements. Identification of elements to receive can either be done by unique Openstreetmap ID or by parameters to search for. This, for example, may be the name of the element or simply its distance to a specific point, that has to fall below a cetain value.\newline

		 In dependence of its implementation, data storage is done in memory (\texttt{MemoryDataSet}), on disc or in a database.
	
	\item Interface \texttt{IRouter}

		\texttt{IRouter} is the interface which has to be implemented by any routing class. Its primary task is triggered by calling the \texttt{route(...)} method, which performs routing between a point to start from an one or more destination points. One has to pass an \texttt{IDataSet} object specifying routing resources, when calling \texttt{route(...)}. The router is to return a \texttt{Route} object containing detailed information about the path.\newline
		
		Traveling Salesman provides several implementations of the \texttt{IRouter} interface using different routing algorithms. The \texttt{MultiTargetDijkstraRouter} can be considered as the default implementation. As implied by its name, it is based on the Dijkstra algorithm which is extended to an A*-algorithm by using the linear distance to the target node as a heuristic. Its implementation, however, seem to be faulty (see chapter \ref{subsubsec:routing_mobiletsm_structure} for details).
			
	\item Interface \texttt{IRoutingMetric}
	
		As to give the router a  measure of routing costs, one has to define a class implementing the \texttt{IRoutingMetric} interface, which allows the router to query routing costs of particular routing steps.\newline
		
		The default implementation (\texttt{ShortestRouteMetric}) simply measures distance between start and end of a routing step by summing up the linear distances between nodes on the way. One might feel uncomfortable with this, because it does not privilege any type of street and hence the shortest route is probably not the fastest one. However, this can be overcome with a re-implementation of a routing metric.
	
\end{itemize}

To represent Openstreetmap map elements (nodes, ways and relations), Traveling Salesman uses classes provided by Osmosis, which can be considered as a Java based framework for processing of Openstreetmap data. Osmosis employs classes named \texttt{Node}, \texttt{Way} and \texttt{Relation} to represent Openstreetmap map elements accordingly.

